Section_8_Team1_Lab2_Report

### 2021-08-03 reports/Draft_Report.Rmd
report adds- operationalization and model updates

@@

```{r dataframe, echo=FALSE}
df <- read.csv('~/lab-2-lab2_section8_jal/data/interim/covid_trips_interim.csv')
head(df)

@@

ggplot(df, aes(x=total_pop)) + geom_histogram(bins=100) 
ggplot(df, aes(x=sum_cases)) + geom_histogram(bins=100)
ggplot(df, aes(x=sum_deaths)) + geom_histogram(bins=100) 
ggplot(df, aes(x=long_trip)) + geom_histogram(bins=100)

@@

model <- lm(, data = )
model2 <- lm(, data = )
model3 <- lm(, data = ) #final model

>>>>

To create our dataframe, we cleaned and filtered data from multiple sources of data and joined based on texas county name or code.

#### Operationalization of focus variables
We gathered covid case and death data from NYT. We gathered trip distance data from the Bureau of Transportation, which they record based on data gathered from personal mobile devices. This data was presented as number of travelers in binned distances. We defined a short trip as less than 100 miles and long trips as greater than 100 miles. This was decided under the assumption that distances traveled of less than 100 miles are for the purpose of commuting, while greater than 100 miles indicated vacation travel.

#### Operationalization of additional variables
To enrich our model and limit OVB, we brainstormed a number of additional variables that could affect travel rates during covid. For one, we looked at location due to the assumption that those who live in rural settings are likely to commute farther than those in an urban setting. We also looked at age, gender, income demographics. Finally, we pulled in data for county population to normalize all the data on a per capita basis.

@@

```{r dataframe, echo=FALSE}
df <- read.csv('/home/jovyan/r_bridge/code/lab-2-lab2_section8_jal/data/interim/covid_trips_interim.csv')
head(df)

@@

ggplot(df, aes(x=total_pop)) + geom_histogram(bins=100))
ggplot(df, aes(x=sum_cases)) + geom_histogram(bins=100)
ggplot(df, aes(x=sum_deaths)) + geom_histogram(bins=100) 
ggplot(df, aes(x=long_trip)) + geom_histogram(bins=100)

@@

#need to change these to per capita data
model1 <- lm(long_trip ~ cases + deaths, data = df) #limited model
model2 <- lm(, data = )
model3 <- lm(, data = ) #final model

#Run F test to show statistical significance of additional variables
anova(model1, model2, test = "F")
anova(model2, model3, test = "F")

#Run coeftest to show statistical significanve of all variables in the model
coeftest(model3, vcov = vcovHC(model3, type="HC1"))
```
